A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-19 writeup/paper.tex

%%%%%%%%%%%%%%% MAP OF WORKER LOCATIONS %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=\linewidth]{figures/turkermap-full}
\caption{The number of workers per country.  This map was generated based on geolocation of IP address of the 5284 workers in our study.  The size of the circles represents the number of worker from each country.  The two largest are India (2022 workers) and the United States (904).  To calibrate the sizes: the Philippines has 147 workers, Egypt has 25, Russia has 10, and Sri Lanka has 4.}
\label{map}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Background and Related Work}
%\section{Background on Mechanical Turk and Related Work}
%\section{Mechanical Turk}
Amazon's Mechanical Turk (MTurk) is an online marketplace for work which gives employers and researchers access to a large, low-cost, human workforce. MTurk provides a simple interface for accessing human skill, allowing requesters to provide micro-payments in return for workers completing micro-tasks.  The basic units of work on MTurk are called ``Human Intelligence Tasks'' (HITs), which suggests that it was designed to accommodate tasks that are difficult for computers, but simple for people. This allows for research into human computation, where people can be treated as a function call \cite{vonAhn2008,Little2009,quinn-bederson:2011}, as well as for large-scale annotation of training data for machine learning applications, including computer vision \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10} and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK}.

On MTurk researchers who need work completed are called `Requesters', workers are often referred to as `Turkers', and micro tasks are called `HITs'.  MTurk is a true market, meaning that Turkers are free to choose to complete the HITs which interest them, and Requesters can price their tasks competitively to try to attract workers and complete have their tasks done quickly \cite{faridani-et-al:2011,singer-mittal:2011}. Turkers' identities remain anonymous to Requesters, and all payment occurs through Amazon. Requesters are able to accept submitted work or reject work that they do not feel meets their standards.  Turkers are only pay if a Requester accepts their work.

Several reports examine Mechanical Turk as a marketplace \cite{ipeirotis:2010:marketplace,lehdonvirta-ernkvist:2011}.  When Amazon introduced MTurk, it first offered payment only in Amazon credits, and later offered direct payment in US dollars. More recently has expanded to include one foreign currency, the Indian rupee. Despite its payments being limited to two currencies or Amazon credits, MTurk claims over half a million workers from 190 countries.\footnote{https://requester.mturk.com/tour}  This suggest that it has a diverse worker population that should represent a wide variety of languages.

@@

Typically, researchers rely on large amounts of MTurk data in order to compensate for the high likelihood of low quality labels. Snow et al. describes the success of using redundant non-expert labels to substitute for professional annotations, achieving comparable quality for much lower cost. The tasks from which these conclusions were drawn, however, were kept simple and easily-verifiable, with annotations restricted to either multiple choice or bounded numeric inputs. As NLP research advances, the level of expertise required from annotators advances as well. Callison-Burch et al. report success using MTurk to build parallel corpora for Machine Translation, a task which requires Turkers to speak two languages with a high level of proficiency.

@@

>>>>

%%%%%%%%%%%%%%% MAP OF WORKER LOCATIONS %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=\linewidth]{figures/turkermap-color-cropped}
\caption{The number of workers per country.  This map was generated based on geolocating the IP address of the 5,284 workers in our study.  The size of the circles represents the number of worker from each country.  The two largest are India (2,022 workers) and the United States (904).  To calibrate the sizes: the Philippines has 147 workers, Egypt has 25, Russia has 10, and Sri Lanka has 4.}
\label{map}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Background and Related Work}
%\section{Background on Mechanical Turk and Related Work}
%\section{Mechanical Turk}
Amazon's Mechanical Turk (MTurk) is an online marketplace for work which gives employers and researchers access to a large, low-cost, workforce. MTurk provides a simple interface for accessing human skills, allowing employers to provide micro-payments in return for workers completing micro-tasks.  The basic units of work on MTurk are called ``Human Intelligence Tasks'' (HITs).  MTurk was designed to accommodate tasks that are difficult for computers, but simple for people. This facilitates research into human computation, where people can be treated as a function call \cite{vonAhn2008,Little2009,quinn-bederson:2011}.  It has application to other fields like human-computer interaction \cite{bigham-et-al:2010,bernstein-et-al:2010}, computer vision  \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10}, speech processing \cite{novotney-callisonburch:2010:NAACLHLT,Eskenazi:2013:crowdsourcing-speech-book},  and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK}.

On MTurk, researchers who need work completed are called `Requesters', workers are often referred to as `Turkers', and micro tasks are called `HITs'.  MTurk is a true market, meaning that Turkers are free to choose to complete the HITs which interest them, and Requesters can price their tasks competitively to try to attract workers and complete have their tasks done quickly \cite{faridani-et-al:2011,singer-mittal:2011}. Turkers' identities remain anonymous to Requesters, and all payment occurs through Amazon. Requesters are able to accept submitted work or reject work that they do not feel meets their standards.  Turkers are only pay if a Requester accepts their work.

Several reports examine Mechanical Turk as an economic market \cite{ipeirotis:2010:marketplace,lehdonvirta-ernkvist:2011}.  When Amazon introduced MTurk, it first offered payment only in Amazon credits, and later offered direct payment in US dollars. More recently has expanded to include one foreign currency, the Indian rupee. Despite its payments being limited to two currencies or Amazon credits, MTurk claims over half a million workers from 190 countries.\footnote{https://requester.mturk.com/tour}  This suggest that its worker population that should represent a diverse set of languages.

@@

%Typically, researchers rely on large amounts of MTurk data in order to compensate for the high likelihood of low quality labels. Snow et al. describes the success of using redundant non-expert labels to substitute for professional annotations, achieving comparable quality for much lower cost. The tasks from which these conclusions were drawn, however, were kept simple and easily-verifiable, with annotations restricted to either multiple choice or bounded numeric inputs. As NLP research advances, the level of expertise required from annotators advances as well. Callison-Burch et al. report success using MTurk to build parallel corpora for Machine Translation, a task which requires Turkers to speak two languages with a high level of proficiency.

@@

\newcite{irvine:10} Using Mechanical Turk to annotate lexicons for less commonly used languages

 MTurk to build parallel corpora for Machine Translation, a task which requires Turkers to speak two languages with a high level of proficiency.
\cite{ambati_act,ambati_naacl,bloodgood-callisonburch:2010:ACL,zaidan-callisonburch:2011:ACL-HLT2011a,Zbib-etal:2012:NAACL,post-callisonburch-osborne:2012:WMT}
